---
title: "Homework 3: lubridate and purrr"
author: "Sloane Johns"
date: "2025-02-25"
output: html_document
---
&nbsp;  
```{r, message=FALSE}
# libraries
library(tidyverse)
library(lubridate)
library(purrr)
```
&nbsp;  

### Exercise 1: Advanced Date Manipulation with lubridate
&nbsp;  
Generate a sequence of dates from **January 1, 2015** to **December 31, 2025**, spaced by every **two months**. Extract the **year**, **quarter**, and **ISO week number** for each date.
```{r}
# Generate a sequence of dates spaced by 2 months
date_seq <- seq(ymd("2015-01-01"), ymd("2025-12-31"), by = "2 months")

# extract year
date_seq %>% year()

# extract quarter
date_seq %>% quarter()

# extract ISO week number
date_seq %>% isoweek()
```
&nbsp;

### Exercise 2: Complex Date Arithmetic
&nbsp;  
Given the following dates, compute the difference in **months** and **weeks** between each consecutive pair.
```{r}
sample_dates <- c("2018-03-15", "2020-07-20", "2023-01-10", "2025-09-05")
sample_dates <- ymd(sample_dates)

# difference in months
diff1_month <- interval(sample_dates[1], sample_dates[2]) %/% months(1)
diff2_month <- interval(sample_dates[3], sample_dates[4]) %/% months(1)

# difference in weeks
diff1_week <- interval(sample_dates[1], sample_dates[2]) %/% weeks(1)
diff2_week <- interval(sample_dates[3], sample_dates[4]) %/% weeks(1)

# print
print(paste("The difference between", sample_dates[1], "and", sample_dates[2], "is", diff1_month, "months."))
print(paste("The difference between", sample_dates[3], "and", sample_dates[4], "is", diff2_month, "months."))
print(paste("The difference between", sample_dates[1], "and", sample_dates[2], "is", diff1_week, "weeks."))
print(paste("The difference between", sample_dates[3], "and", sample_dates[4], "is", diff2_week, "weeks."))
```
&nbsp;

### Exercise 3: Higher-Order Functions with purrr
&nbsp;
Using `map()` and `map_dbl()`, compute the **mean**, **median**, and **standard deviation** for each numeric vector in the following list:
```{r}
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))

# mean
num_lists %>% map(mean)

# median
num_lists %>% map(median)

# standard deviation
num_lists %>% map(sd)

```

